PANCHANGE_data_preprocessing

### 2020-08-24 PANCHANGE_data_preprocessing2020-07-15.Rmd

Calculate the time difference between sign up questionnaire and COPING questionnaire
```{r time difference between sign up questionnaire and COPING questionnaire}
if(GLAD == TRUE | EDGI == TRUE){
dat <- dat %>%
  mutate(
    time_diff_sign_up_coping =
        as.numeric(
        difftime(           #this function does time1 - time2 as difftime(time1, time2...)
          startDate.coping,    #should be start date for COPING (time1)
          startDate.prepandemic),    #should be start date for GLAD (time2)
          units = c("days")  #can also be "secs", "mins", "hours", "weeks"
          )
        )

>>>>

Calculate the time difference between sign up questionnaire and COPING questionnaire
```{r time difference between sign up questionnaire and COPING questionnaire}
if(GLAD == TRUE | EDGI == TRUE){
dat <- dat %>%
  mutate(
    time_diff_sign_up_coping =
        as.numeric(
        difftime(           #this function does time1 - time2 as difftime(time1, time2...)
          startDate.coping,    #should be start date for COPING (time1)
          startDate.prepandemic),    #should be start date for GLAD (time2)
          units = c("weeks")  #can also be "secs", "mins", "hours", "weeks"
          )
        )
